---
title: "Developing Data Products - Assignment Week 3"
author: "Simon Rodriguez"
date: "October 24, 2017"
output: ioslides_presentation
---

```{r setup, echo = F, message=F, warning=F, include=FALSE}
```

## Geolocation and height of peaks higher than 1500m around the world

In the next slide we will see a plot of most of the highest peaks in the world. Some locations can be easily recognised even though there is not a map under the locations of the peaks, such as South America due to the Andes and Nepal with the Himalayas. 

Hovering each peak will display its name and height. Also, the color coding gives a quick idea of the height range of said peak (green is for the small cases, red is for the highest ones).

If you want to download the database I used, go to:
 http://viewfinderpanoramas.org/prominence.html

## Geolocation and height of peaks higher than 1500m around the world

```{r processing, echo = F, message=F, warning=F}
setwd("/home/simon/Desktop/")

# Locations and names of mountains all around the world higher than 1500m
places <- read.csv("1500.csv", header = T)
places$Lat_dec = as.numeric(as.character(places$Lat_dec))
places$Long_dec = as.numeric(as.character(places$Long_dec))
places["Class"] <- c()
attach(places)

# Create the color codes
places$Class[(Elevation >= 8000)] <- ">8000m"
places$Class[(Elevation >= 7000) & (Elevation < 8000)] <- ">7000m"
places$Class[(Elevation >= 6000) & (Elevation < 7000)] <- ">6000m"
places$Class[(Elevation >= 5000) & (Elevation < 6000)] <- ">5000m"
places$Class[(Elevation >= 4000) & (Elevation < 5000)] <- ">4000m"
places$Class[(Elevation >= 3000) & (Elevation < 4000)] <- ">3000m"
places$Class[(Elevation >= 2000) & (Elevation < 3000)] <- ">2000m"
places$Class[Elevation < 2000] <- ">1500m"

# Name + height column
places$info = paste(places$Name, "-", paste0(places$Elevation,"m"))

# Create the new (clean) dataframe
newPlaces <- data.frame(lat = places$Lat_dec, lng = places$Long_dec, class = places$Class, info = places$info, height = places$Elevation)

```

```{r plot, echo = F, warning=F, message=F}
library(plotly)

g <- list(
  scope = 'world',
  showland = TRUE,
  landcolor = toRGB("gray95"),
  subunitcolor = toRGB("gray85"),
  countrycolor = toRGB("gray85")
)

p <- plot_ly(newPlaces, x = ~lng, y = ~lat) %>%
    add_markers(text = ~info, color = ~class, symbol = I("triangle-up"), size = I(8), hoverinfo = "text",   colors=c("green","red"), size=20 , opacity=0.5) 
p
```

## Thanks!

